Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-18 documents/mixtures/mixture_models.tex
fractional residual plots for log

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile.png}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{exp_K06_MR08_residual.png}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_residual_log.png}
\caption{\textsl{top-left:} The true exp profile (thin black line),
  the best $M^{\exp}=6$ mixture-of-Gaussian approximation (thick grey
  line), and the component Gaussians (multiplied by their
  corresponding amplitudes) contributing to the approximation (thin
  grey lines).  The plot title text gives $\xi_{\max}$ and the
  badness. \textsl{top-right:} The same but shown logarithmically.
  \textsl{bottom-left:} A representation of the residual or devation,
  on which the badness is computed.  \textsl{bottom-right:} The same
  but shown logarithmically.\label{fig:exp}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual_log.png}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.
  The residuals look bad in the logarithmic plot, but they are only
  bad very near the profile center (as expected), where the effect of
  any realistic point-spread function will average them away.}
\end{figure}

>>>>

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile.png}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{exp_K06_MR08_residual.png}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_fractional_log.png}
\caption{\textsl{top-left:} The true exp profile (thin black line),
  the best $M^{\exp}=6$ mixture-of-Gaussian approximation (thick grey
  line), and the component Gaussians (multiplied by their
  corresponding amplitudes) contributing to the approximation (thin
  grey lines).  The plot title text gives $\xi_{\max}$ and the
  badness. \textsl{top-right:} The same but shown logarithmically.
  \textsl{bottom-left:} A representation of the residual or devation,
  on which the badness is computed.  \textsl{bottom-right:} The same
  but shown fractionally and logarithmically.\label{fig:exp}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_fractional_log.png}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.
  The residuals look bad in the logarithmic plot, but they are only
  bad very near the profile center (as expected), where the effect of
  any realistic point-spread function will average them away.}
\end{figure}
